Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-09-01 supplement.tex
cleaned up captions

\begin{figure}[ht!]
    \centering
    \includegraphics[width=5in]{figures/supp-SE-merged-data}
    \caption{
        \textbf{Average error of statistics from low coverage and merged datasets.}
        Low coverage data provides consistent allelic diversity and linkage
        disequilibrium measures to high coverage data. On the other hand,
        merging separately called datasets can lead to large discrepancies
        in computed LD statistics.
    }
    \label{fig:supp-merged-data-SEs}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/supp-merged-data-model-fits}
    \caption{
        \textbf{Merged datasets bias demographic inferences.}
        While statistics from low and high coverage datasets provide consistent
        best-fit demographic models, merged datasets result in biased LD
        statistics (Figure~\ref{fig:supp-merged-data-SEs}). These biased LD
        statistics lead to large downstream biases in inferred demographic
        models.
    }
    \label{fig:supp-merged-data-fits}
\end{figure}

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=5in]{figures/supp-SE-merged-data}
    \caption{
        \textbf{Average error of statistics from low coverage and merged datasets.}
        Low coverage data provides allelic diversity and linkage
        disequilibrium measures consistent with those from high coverage data (left panel). On the other hand,
        merging separately called datasets can lead to large discrepancies
        in computed LD statistics (middle and right panels).
    }
    \label{fig:supp-merged-data-SEs}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/supp-merged-data-model-fits}
    \caption{
        \textbf{Merged datasets bias demographic inferences.}
        The panels represent best-fit models according to 
        different combinations of high- and low- coverage data.
        While statistics from low and high coverage datasets provide consistent
        best-fit demographic models, merged datasets result in biased LD
        statistics (Figure~\ref{fig:supp-merged-data-SEs}). These biased LD
        statistics lead to large downstream biases in inferred demographic
        models. 
    }
    \label{fig:supp-merged-data-fits}
\end{figure}
